### 2023-10-23 chapters/paper_benchmarking.tex
Improve table layout

    \caption[Model likelihoods and phoneme error rate for TIMIT.]{ We report model likelihoods $\mathcal{L}$ for TIMIT represented as a 16bit $\mu$-law encoded PCM for different stochastic latent variable models and deterministic autoregressive baselines (left) and phoneme error rate (PER) of different representations for phoneme recognition on TIMIT (right).}

@@

    \begin{subtable}[t]{.49\textwidth}

>>>>

    \caption[Model likelihoods and phoneme error rate for TIMIT.]{ We report model likelihoods $\mathcal{L}$ for TIMIT represented as a $\SI{16}{bit}$ $\mu$-law encoded PCM for different stochastic latent variable models and deterministic autoregressive baselines (left) and phoneme error rate (PER) of different representations for phoneme recognition on TIMIT (right).}

@@

    \begin{subtable}[t]{.485\textwidth}
